%!TeX program = pdflatex
% Geoff Boeing's Curriculum Vitae
% Email: boeing@usc.edu
% Web: https://geoffboeing.com/
% Repo: https://github.com/gboeing/cv

\documentclass[11pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) for accented characters as single glyph
\usepackage[cmintegrals,cmbraces]{newtxmath}
\usepackage{ebgaramond-maths}
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % regionalize hyphens, quote marks, etc automatically
\usepackage{microtype}% improve text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto}    % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts
\usepackage{setspace} % custom line spacing

% what is your name?
\newcommand{\myname}{Mikhail Kornev}

% select default typefaces
\usepackage{ebgaramond} % document's serif typeface
\usepackage{tgheros}    % document's sans serif typeface

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{4cm}

% define font to use as document's title
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*, family=\sfdefault}{30} % increase sans serif headings tracking
\titleformat{\section}{\lsstyle\sffamily\small\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{30pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{16pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

% set page margins (assumes letter paper)
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% set line spacing
\setstretch{0.9}

% define space between list items
\newcommand{\listitemspace}{0.25em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print only the month and year when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    citecolor   = black,
    linkcolor   = black,
    pdfauthor   = {\myname},
    pdfkeywords = {city planning, housing, street networks, transportation, urban design, urban informatics},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
    \raggedright{}

    % display your name as the document title
    \namefont{\myname}

    % affiliation and contact info blocks
    \vspace{1em}
    \begin{minipage}[t]{2.5in}
        % current primary affiliation, left-aligned
        Steklov Mathematical Institute of RAS 
    \end{minipage}
    \hfill
    \begin{minipage}[t]{3in}
        % contact info details, right-aligned
        Nationality: Russian\\
        E-mail: \href{mailto:michaelkorneff@gmail.com}{\tt michaelkorneff@gmail.com}\\
        Web-page: \href{https://magisterlud.github.io}{\tt https://magisterlud.github.io}
    \end{minipage}
    
    \section*{Research Areas}

   Homotopy Theory, Higher Geometry, Group Theory, and Combinatorics    
    
    
    
     \section*{Appointments}

    \begin{tablist}

        \item[Sep. 2022 --]   \tab{}PhD student and research assistant at Steklov Mathematical Institute of RAS  \\
                              Department of Geometry and Topology

        \item[Sep. 2021 --]  \tab{}Research assistant at HSE University \\
                              Laboratory of Algebraic Topology and Applications

    \end{tablist}




    \section*{Education}

    \begin{tablist}

        \item[Sep. 2016 -- May 2022]  \tab{}Specialist degree Diploma with honors in Mathematics (equivalent to M.S.)\\ Lomonosov Moscow State University 

    \end{tablist}
    
    
    
    
    
    
      \section*{Papers}

    \begin{tablist}
	
	\item[May 2025] \tab{Joint work with Victor Buchstaber}\\ {\it $n$-Valued Groups, Kronecker Sums, and Wendt's $(x, y, z)$-Matrices}\\ arXiv: 2505.04296
        \item[Jan. 2024] \tab{}{\it $n$-Valued Coset Groups and Dynamics}\\ arXiv: 2401.12718\\ Math. Notes, 116:1 (2024), 66–76., 2024
        \item[Sep. 2023] \tab{}{\it Homology Spheres}\\ Proceedings of Moscow Mathematical Society, 84:2 (2023),  243–296
        
    \end{tablist}
    
    
        
    
    
    
    
    
     \section*{Conference Talks}

    \begin{tablist}
    
       \item{May 2025} \tab{}{\it Number-Theoretic Problems in Algebraic Topology}\\ Joint work with Victor Buchstaber\\ XXIV Intrenational Conference
``Algebra, Number Theory, Discrete Geometry and Multiscale Modeling.
Modern Problems, Applications and Problems of History''
dedicated to the 110th anniversary of the birth of academician Yu. V. Linnik
and the 110th anniversary of the birth of professor A. B. Shidlovsky
and the 80th anniversary of the birth of professor G. I. Arkhipov, Tula, Russia
       
         
       \item{May 2024} \tab{}{\it Homology Spheres, Acyclic Groups and Kan-Thurston Theorem}\\ Conference ``From Analysis to Homotopy Theory'' , University of Greifswald, Greifswald, Germany 
    
       \item{April 2023} \tab{}{\it Dynamics and multivalued groups}\\ Conference 	``SIMC Youth Race'', Steklov Mathematical Institute of RAS, Moscow, Russia
       
        \item{Oct. 2022} \tab{}{\it Inconcretness of homotopy categories}\\ International School ``Toric topology, combinatorics and data analysis'', Euler International Mathematical Institute, Saint Petersburg, Russia
       
       \item{April 2022} \tab{}{\it Acyclic groups and spaces}\\ 29th International Scientific Conference for Undergraduate and Graduate Students and Young Scientists ``Lomonosov'', Moscow, Russia
       
         \item{Nov. 2021} \tab{}{\it Acyclic groups and Kan-Thurston theorem}, International School
``Toric Topology and Combinatoric'', Sirius Mathematics Center, Sochi, Russia
          
    \end{tablist}
    
    
    
    
    
    \section*{Seminar Talks}
      
      \begin{tablist}
      
      \item{May 2025} \tab{}{\it $n$-Valued Groups, Kronecker Sums, and Wendt Matrices}\\ Joint work with Victor Buchstaber\\ Seminar of the Department of Geometry and Topology ``Geometry, Topology and Mathematical Physics'', Steklov Mathematical Institute of RAS (Novikov Seminar), Moscow, Russia
      
       \item{April 2023} \tab{}{\it Acyclic groups and Kan-Thurston theorem}\\ Seminar by I. G. Lysenok and A. L. Talambutsa ``Seminar on geometric group theory'', Steklov Mathematical Institute of RAS, Moscow, Russia
       
       \item{Dec. 2022} \tab{}{\it Fundamental groups of homology spheres}\\ Seminar ``Geometry, Topology and their applications'' at Sobolev Institute of Mathematics
       
      
    \end{tablist}

    
    
    
    
     \section*{Grants and Awards}

    \subsection*{Prizes, fellowships and grants}

    \begin{tablist}

        \item[2021 --] \tab{}{\it The Russian Science Foundation Grant No. 23-11-00143} 
        \item[2019] \tab{}{\it Winner of the olympiad on Partial Differential Equations}\\ Lomonosov Moscow State University
        \item[2018] \tab{}{\it Winner of the olympiad on Ordinary Differential Equations}\\ Lomonosov Moscow State University

    \end{tablist}


    
    
        
       
    
    
    
    
    \section*{Study Seminar Talks}
    
    \subsection*{\href{https://researchseminars.org/seminar/HomotopyTheoryAndApps}{Texas Tech Quantum Homotopy Seminar}}
    
    \begin{tablist}
    
    \item{Dec. 2024} \tab{\it An Introduction to Cartan Geometries}
    
     \item{Mar. 2024} \tab{\it Euler-Lagrange dynamics via the $\infty$-jet bundle} (2 talks)
     
     \end{tablist}
    
    \subsection*{\href{https://researchseminars.org/seminar/HomotopyTheoryAndApps}{Seminar On Homotopy Theory And Applications At Independent University Of Moscow}}
    
     \begin{tablist}
     
     \item{Dec. 2023} \tab{\it Principal $\infty$-bundles}
     
     \item{Apr. -- May 2023} \tab{\it A mini-course on the $\infty$-category of motivic coarse spaces} (4 talks)
     
     \item{April 2023} \tab{}{\it Elements of unstable motivic homotopy theory}
     
     \item{Feb. -- Apr. 2023} \tab{}{\it A mini-course on $\infty$-cosmoi} (4 talks)
     
     \item{Dec. 2022} \tab{}{\it Applications of Reedy theory}
     
     \item{Nov. 2022} \tab{}{\it Weighted (co-)limits, Gambino's theorem, Reedy model structures}
     
     \item{Nov. 2022} \tab{}{\it Homotopically final functors and examples of calculations with homotopy (co-)limits}
     
     \item{Nov. 2022} \tab{}{\it Nerve—realization adjunction and bar construction}
     
     \item{April 2022}  \tab{}{\it A series of 4 talks on sheaves of sets}
     
     \item{April 2022} \tab{}{\it Kan extensions. Additional topics}
     
     \item{Oct. 2021} \tab{}{\it The categorical meaning of the Kan-Thurston theorem} 
     
     \item{Jul. -- Aug. 2021} \tab{}{\it Quillen's theorem, a closed model structure on $s\mathcal{Set}$}
     
     \end{tablist}
     
     \subsection*{Study And Scientific Seminar ``Geometry And Topology'' At Lomonosov Moscow State University}
     
     \begin{tablist}
     
     \item{Sep. 2020} \tab{}{\it Andreev's theorem on hyperbolic polyhedra}
     
     \item{Nov. 2019} \tab{}{\it The intersection form of 4-manifolds}
     
     \item{May 2019} \tab{}{\it Nilmanifolds and Massey product in bigraded cohomology rings}
      
     \end{tablist}
    
    
    
    
    \section*{Conferences, Workshops and Schools}
      
      \begin{tablist}
       
      \item{May 2024} \tab{}{\it Conference ``From Analysis to Homotopy Theory''}\\ University of Greifswald, Greifswald, Germany 
      
      \item{Jul. 2023} \tab{}{\it Summer School ``Algebra and Geometry''}\\ HSE University, Steklov Mathematical Institute of RAS, Suzdal, Russia
      
      \item{Jul. 2023}  \tab{}{\it Summer school on non-commutative and derived geometry of matrix factorisations}\\ Centre of Pure Mathematics, Moscow Institute of Physics and Technology, Dolgoprudny, Russia
      
      \item{Jun. 2023} \tab{}{\it Conference on algebra, algebraic geometry, and number theory on the occasion of academician Igor Rostislavovich Shafarevich 100th birthday}\\ Steklov Mathematical Institute of RAS, Moscow, Russia
      
      \item{Apr. 2023} \tab{}{\it Conference ``Geometry, topology and mathematical physics'' on the occasion of the 85th anniversary of S. P. Novikov and the 80th anniversary of V. M. Buchstaber}\\ Steklov Mathematical Institute of RAS, Moscow, Russia
      
      \item{Mar. 2023} \tab{}{\it Conference ``SIMC Youth Race''}\\ Steklov Mathematical Institute of RAS, Moscow 
      
      \item{Oct. 2022} \tab{}{\it International School ``Toric topology, combinatorics and data analysis''}\\ Euler International Mathematical Institute, Saint
Petersburg, Russia
      
      \item{Jul. 2022} \tab{}{\it Summer School ``Algebra and Geometry''}\\ HSE University, Steklov Mathematical Institute of RAS, Suzdal, Russia
      
      \item{Apr. 2022} \tab{}{\it 29th International Scientific Conference for Undergraduate and Graduate Students and Young Scientists ``Lomonosov''}\\ Lomonosov Moscow State University, Moscow, Russia
      
      \item{Nov. 2021} \tab{}{\it International School ``Toric Topology and Combinatorics''}\\ HSE University, Sirius Mathematics Center, Sochi, Russia  
      
       \item{Nov. 2020} \tab{}{\it Topology and Geometry of Group Actions}\\ HSE University, online
       
       \item{Nov. 2019} \tab{}{7th Summer School On Geometrical Methods Of Mathematical Physiques}\\ Landau Institute for Theoretical Physics, Lomonosov Moscow State University, Chernogolovka, Russia
       
       \item{Nov. 2019} \tab{}{\it Geometry, Topology And Mathematical Physics}\\ Landau Institute for Theoretical Physics, Lomonosov Moscow State University, Chernogolovka, Russia
       
        \item{Nov. 2018} \tab{}{\it Geometry, Topology And Mathematical Physics}\\ Landau Institute for Theoretical Physics, Lomonosov Moscow State University, Chernogolovka, Russia
       
       \item{Jul. 2018} \tab{}{\it Summer school ``Modern Mathematics''}\\ HSE University, Lomonosov Moscow State University, Independent University of Moscow, Dubna, Russia
       
        \item{Jul. 2017} \tab{}{\it Summer school ``Modern Mathematics''}\\ HSE University, Lomonosov Moscow State University, Independent University of Moscow, Dubna, Russia
        
            
    \end{tablist}

    
    
    
    
    \section*{Teaching}

    \begin{tablist}
    
       \item{May 2022 --} \tab{}{\it Teaching various courses (e. g., Algebraic Geometry, Algebraic Topology, Abstract Algebra, Differential Geometry, Linear Algebra, Probability Theory, Discrete Mathematics, Calculus, etc.) on Profi}\\ \href{https://profi.ru/profile/KornevMI3/}{\tt https://profi.ru/profile/KornevMI3/} 

        \item{Sep. 2016 -- 2022} \tab{}{\it Little Mech-Math courses}\\ An olympiad Math class at Lomonosov Moscow State University\\ \href{http://mmmf.msu.ru/about/person.html}{\tt http://mmmf.msu.ru/about/person.html}
        
    \end{tablist}
    
    
   




    \section*{Service}

    \begin{tablist}

       \item{June 2021 --} \tab{}{\it Co-organization of the study seminar ``Homotopy Theory and Applications'' at Independent University of Moscow}\\ \href{https://researchseminars.org/seminar/HomotopyTheoryAndApps}{\tt https://researchseminars.org/seminar/HomotopyTheoryAndApps} 

    \end{tablist}
    
    
    
    
    
    \section*{References}

    \begin{itemize}

       \item[] {\it Victor Buchstaber}, Steklov Mathematical Institute of RAS\\ \href{mailto:buchstab@mi-ras.ru}{\tt buchstab@mi-ras.ru} 

    \end{itemize}
    
    
    
    
    
     \section*{Languages}

    \begin{itemize}

       \item[] {\it Russian} (native)
       \item[] {\it English} (fluent)
       \item[] {\it French} (intermediate)
       \item[] {\it Latin} (basic)

    \end{itemize}

  

      


\end{document}
